---
title: "ml"
author: "testcourse"
date: "Sunday, September 21, 2014"
output: html_document
---

# Agenda  
 1.Analyze the data and extract the feature  
 2.Predict the result of the test



## Analyze the data and extract the feature  
```{r echo=FALSE, cache=TRUE}
train <- read.csv("pml-training.csv")
test <- read.csv("pml-testing.csv")
```

1. We can easily discard some attributes because they have little valid values, such as kurtosis_roll_belt,kurtosis_picth_belt,kurtosis_yaw_belt, and so on
2. We can also discard some attributes because they make no or little differences, such as
```{r echo=FALSE}
table(train$user_name, train$classe)
```  
3. We need to find all the features that make a lot difference, such as raw_timestamp_part_1 and raw_timestamp_part_1  
Take raw_timestamp_part_1 as an example, for a particular raw_timestamp_part_1
```{r echo=FALSE}
table(train$raw_timestamp_part_1, train$classe)
```  
Finally, I decide to use these attributes as features:  
  aw_timestamp_part_1  
  raw_timestamp_part_2  
  num_window  
  total_accel_belt  
  total_accel_forearm  
  
  
Beault the model  
```{r cache=TRUE, results='hide'}
require(e1071)
model <- svm(classe ~ raw_timestamp_part_1 + raw_timestamp_part_2 + num_window + total_accel_belt + total_accel_forearm, data = train)
```

## Predict the result  
```{r}
require(e1071)
result <- predict(model, newdata=test[,c("raw_timestamp_part_1","raw_timestamp_part_2","num_window","total_accel_belt","total_accel_forearm")])
result
```  






